---
title: "Ben Analysis"
output: html_document
---
```{r}
library(tidyverse) 
library(tidymodels)
library(openintro)
```


```{r create-EU-non_EU-vector}

x <- c("non-EU", "non-EU", "EU", "non-EU", "EU", "EU", "EU", "EU", "Outside-Europe", "Outside-Europe", "EU", "EU", "EU", "Outside-Europe", "EU", "EU", "EU", "EU", "Outside-Europe", "EU", "EU", "EU", "EU", "non-EU", "EU", "EU", "EU", "EU", "EU")
```


```{r adding-new-column-of-EU-nonEU}
combined$NonEU_EU <- x
```

```{r counting-EU-nonEU-countries}
combined %>%
  count(NonEU_EU)
```
Within this combined data-set we have 21 countries out of the 27 that are currently a part of the European Union. For Non-EU European countries, we have only 4 out of 28. 


```{r examining-percent-GDP-and-Happiness-Score}
european_combined %>%
    ggplot(aes(x = PC_GDP, y = `Happiness Score`, color = NonEU_EU)) +
    geom_point() +
    labs(x = "Percent of GDP",
         y = "Happiness Score", 
         title = "Pharmecutical Spending Percent of GDP and Happiness Scores")
```
```{r filtering-data-to-European-Countries }
european_combined <- combined %>%
  filter(NonEU_EU != "Outside-Europe")
```




```{r linear-regresssion-PC_GDP-Happiness-Score}
gdp_happiness_correlation <- 
  linear_reg() %>%
  set_engine("lm") %>%
  fit(`Happiness Score` ~ PC_GDP + factor(NonEU_EU), data = european_combined)
gdp_happiness_correlation
```
```{r r-squared-of-correlation}
glance(gdp_happiness_correlation)$adj.r.squared
```
```{r linear-regresssion-PC_GDP-Happiness-Score}
gdp_happiness_correlation_interaction <- 
  linear_reg() %>%
  set_engine("lm") %>%
  fit(`Happiness Score` ~ PC_GDP * factor(NonEU_EU), data = european_combined)
gdp_happiness_correlation_interaction
```

```{r r-squared-of-correlation-interaction}
glance(gdp_happiness_correlation_interaction)$adj.r.squared
```



```{r plotting-with-line-of-best-fit}
european_combined %>%
    ggplot(aes(x = PC_GDP, y = `Happiness Score`, color = NonEU_EU)) +
    geom_point() +
    geom_smooth(method = "lm", 
              color = "yellow", 
              se = FALSE)
    labs(x = "Percent of GDP",
         y = "Happiness Score", 
         title = "Pharmecutical Spending Percent of GDP and Happiness Scores")
```
```{r finding-linear-regression-GDP-Happiness-Score}
GDP_happiness.lm = lm(`Happiness Score` ~ PC_GDP, data = european_combined) 
GDP_Hapiness.res = resid(GDP_happiness.lm)
GDP_Hapiness.res

```


```{r plotting-residuals}
fit <- lm(`Happiness Score` ~ PC_GDP, data = european_combined) # fit the model
european_combined$predicted <- predict(fit)   # Save the predicted values
european_combined$residuals <- residuals(fit) # Save the residual values
ggplot(european_combined, aes(x = PC_GDP, y = `Happiness Score`)) +
  geom_smooth(method = "lm", se = FALSE, color = "lightgrey") +     # regression line  
  geom_segment(aes(xend = PC_GDP, yend = predicted), alpha = .2) +      # draw line from point to line
  geom_point(aes(color = abs(residuals), size = abs(residuals))) +  # size of the points
  scale_color_continuous(low = "green", high = "red") +             # colour of the points mapped to residual size - green smaller, red larger
  guides(color = FALSE, size = FALSE) +                             # Size legend removed
  geom_point(aes(y = predicted), shape = 1) +
  theme_bw()

### Code sourced from https://www.statology.org/residual-plot-r/
```
A residual is a measure of how well a line fits an individual data point across all of the data points within the model. Examining these makes sure that the linear model is appropriate or not to use with the data. From finding the residuals and also making a plot of them, it is apparent that this data is valid data to use as the residuals were not very large. All were between -1.5 and 1.5. 
```{r}
augmented_fit_lm <- augment(gdp_happiness_correlation$fit)
augmented_fit_lm

newdf <- cbind(european_combined$Country, augmented_fit_lm )
newdf
```
```{r}
ggplot(augmented_fit_lm, mapping = aes(x = .fitted, y = .resid)) +
  geom_point(alpha = 0.5) +
  geom_hline(yintercept = 0, color = "gray", lty = "dashed") +
  labs(x = "Happiness Score", y = "Residuals") 
```


```{r finding-summary-statistics-on-model}
summary(fit)
```


```{r creating-subsets-EU-non_EU}
eu_combined_countries <- combined %>%
  filter(NonEU_EU == "EU")
```
```{r}
non_EU_combined_countries <- combined %>%
  filter(NonEU_EU == "non-EU")
```


```{r finding-correlation-GDP-Happiness_EU_Countries}
gdp_happiness_correlation_EU <- 
  linear_reg() %>%
  set_engine("lm") %>%
  fit(PC_GDP ~ `Happiness Score`, data = eu_combined_countries)
gdp_happiness_correlation_EU
```

```{r r-squared-EU}
glance(gdp_happiness_correlation_EU)$r.squared
```


```{r finding-correlation-GDP-Happiness_NonEU_Countries}
gdp_happiness_correlation_NonEU <- 
  linear_reg() %>%
  set_engine("lm") %>%
  fit(PC_GDP ~ `Happiness Score`, data = non_EU_combined_countries)
gdp_happiness_correlation_NonEU
```
```{r r-squared-nonEU}
glance(gdp_happiness_correlation_NonEU)$r.squared
```

