---
title: "Project proposal"
author: "Overachievers"
output: github_document
---

```{r load-packages, message = FALSE}
library(tidyverse)
library(broom)
```

## 1. Introduction
The World Happiness Report dataset was published by Sustainable Development Solutions Network on Kaggle. The scores and rankings from this dataset were retrieved from the Gallup World Poll. The data we are looking at is a collection of what is defined as the ‘Happiness scores’ which were attributed to a list of `r nrow(data)’ countries. The evaluation poll consisted of several questions which were taken from the Cantril ladder which rank features of quality of life answers from 10 (being the most desirable) and 0 (being the least desirable). The data spans findings from 2013 to 2016 and employs the Gallup weights to make the estimates representative. 

## 2. Data

```{r}
#install.packages("codebook")
```

```{r load-world-happiness-data}
happy2015 <- read_csv("/cloud/project/data/world-happiness/2015.csv")
#happy2016 <- read_csv("/cloud/project/data/world-happiness/2016.csv")
#happy2017 <- read_csv("/cloud/project/data/world-happiness/2017.csv")
#happy2018 <- read_csv("/cloud/project/data/world-happiness/2018.csv")
#happy2019 <- read_csv("/cloud/project/data/world-happiness/2019.csv")
drug <- read_csv("/cloud/project/data/pharmaceutical-drug/pharmaceutical_data_csv.csv")
```

```{r glimpse-2015-dataset}
glimpse(happy2015)
```

```{r glimpse-2016-dataset}
#glimpse(happy2016)
```

```{r glimpse-2017-dataset}
#glimpse(happy2017)
```

```{r glimpse-2018-dataset}
#glimpse(happy2018)
```

```{r glimpse-2019-dataset}
#glimpse(happy2019)
```

```{r glimpse-drug-dataset}
glimpse(drug)
```
## 3. Data analysis plan
#### The comparison groups you will use, if applicable.
How different variables affect the happiness score. Impact of geographical location on the Happiness score. 

#### Very preliminary exploratory data analysis, including some summary statistics and visualizations, along with some explanation on how they help you learn more about your data. (You can add to these later as you work on your project.)

We are currently working on defining these and will add these later as we work on our project. 

#### The statistical method(s) that you believe will be useful in answering your question(s). (You can update these later as you work on your project.)

We will resort to the methods we have explored in class. We will describe the specific methods as we progress through our work.

#### What results from these specific statistical methods are needed to support your hypothesized answer?



