---
title: "What Makes You Happy?"
subtitle: "Examining potential relationship between happiness and other factors"
author: "Overachievers <br> Yueh Qi Chuah, Ben van Paassen, Mathieu Moutou"
institute: "Bates College"
date: "`r Sys.Date()`"
output:
  xaringan::moon_reader:
    css: xaringan-themer.css
    lib_dir: libs
    nature: 
      ratio: "16:9"
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

```{r load-packages, include = FALSE}
# Add any additional packages you need to this chunk
library(tidyverse)
library(tidymodels)
library(palmerpenguins)
library(knitr)
library(xaringanthemer)
library(broom)
library(countrycode)
library(RColorBrewer)
library(tmap)
library(rgdal)
library(leaflet)
library("sf")
library("raster")
library("sp")
#install.packages("rnaturalearth")
library(rnaturalearth)
#install.packages("plotly")
library(plotly)
library(rgeos)
```

```{r setup, include=FALSE}
# For better figure resolution
knitr::opts_chunk$set(fig.retina = 3, dpi = 300, fig.width = 6, fig.asp = 0.618, out.width = "80%")
```

```{r load-data, include=FALSE}
happiness <- read_csv("/cloud/project/data/world-happiness/2015.csv")
drug_spending <- read_csv("/cloud/project/data/pharmaceutical-drug/pharmaceutical_data_csv.csv")
```

```{r cleaning-data-sets, include=FALSE}
drug_spending <- drug_spending %>%
  filter(TIME == 2015) %>%
  mutate(Country = countrycode(LOCATION, "iso3c", "country.name")) %>%
  mutate(Continent = countrycode(LOCATION, "iso3c", "continent"))
```

```{r cleaning-happiness-dataset, include=FALSE}
happiness$Country_title = str_to_title(happiness$Country)

happiness %>%
  mutate(Continent = countrycode(Country_title, "country.name", "continent"))
```

```{r combine-both-dataset, include=FALSE}
combined <- inner_join(happiness, drug_spending, by = "Country")
```

```{r create-EU-non_EU-vector, include=FALSE}

x <- c("non-EU", "non-EU", "EU", "non-EU", "EU", "EU", "EU", "EU", "Outside-Europe", "Outside-Europe", "EU", "EU", "EU", "Outside-Europe", "EU", "EU", "EU", "EU", "Outside-Europe", "EU", "EU", "EU", "EU", "non-EU", "EU", "EU", "EU", "EU", "EU")
```


```{r adding-new-column-of-EU-nonEU, include=FALSE}
combined$NonEU_EU <- x
```

```{r filtering-data-to-European-Countries, include=FALSE}
european_combined <- combined %>%
  filter(NonEU_EU != "Outside-Europe")
```

```{r linear-regresssion-PC_GDP-Happiness-Score, include=FALSE}
gdp_happiness_correlation <- 
  linear_reg() %>%
  set_engine("lm") %>%
  fit(`Happiness Score` ~ PC_GDP + factor(NonEU_EU), data = european_combined)
```

```{r, include=FALSE}
augmented_fit_lm <- augment(gdp_happiness_correlation$fit)

finaldf <- cbind(european_combined$Country, augmented_fit_lm )

```

```{r rename-country-column, include=FALSE}
finaldf <- rename(finaldf, Country = `european_combined$Country`)
```


```{r add-geometry-to-df, include=FALSE}
europe <- ne_countries(continent = 'europe', returnclass="sf")
europe_map_df<- inner_join(finaldf, europe, by = c("Country" = "name"))
```

```{r title-slide-settings, include = FALSE}
style_xaringan(
  title_slide_background_image = "img/happiness.jpeg",
  title_slide_text_color = "#000"
)
```

class: center, middle

## A statement of the overall goal / research question

---

class: left, middle

# Background

*

---

class: inverse, center, middle

# Section title

---

class: left, middle

# Implications

.pull-left[
```{r europe-map, echo=FALSE, warning=FALSE, out.height="30%", out.width="100%"}
map <- ggplot(europe_map_df) +
  geom_sf(aes(fill = .std.resid, geometry = europe_map_df$geometry)) +
  labs(title = "Happiness Score Residuals",
       x = "Longitude",
       y = "Latitude", 
       fill = "residuals") +
  xlim(-40, 50) +
  ylim(20, 85) +
  scale_fill_distiller(palette = "Spectral")

ggplotly(map)
```
]

.pull-right[
* some text goes here
* more texts
* texts
]
---

# Hello World

- Click the `Knit` button to compile your presentation

- Make sure to commit and push all resulting files to your GitHub repo

---

class: inverse, middle, center

# Using xaringan

---

# xaringan

- The presentation is created using the `xaringan` package

- Use `---` to separate slides and `--` for incremental builds

--

- Like this

---

# Layouts

You can use plain text

- or bullet points

.pull-left[
or text in two columns $^*$
]
.pull-right[
- like
- this
]

.footnote[
[*] And add footnotes
]

---

# Code

```{r boring-regression}
# a boring regression
model <- lm(dist ~ speed, data = cars)
tidy(model)
glance(model)
```

---

# Plots

```{r recode-species, echo = FALSE}
# In this chunk I'm doing a bunch of analysis that I don't want to present 
# in my slides. But I need the resulting data frame for a plot I want to present.
iris_modified <- iris %>%
  mutate(Species = fct_other(Species, keep = "setosa"))
```

```{r plot-iris, echo = FALSE}
# Code hidden with echo = FALSE
# Uses modified iris dataset from previous chunk
# Play around with height and width until you're happy with the look
ggplot(data = iris_modified, mapping = aes(x = Sepal.Width, y = Sepal.Length, color = Species)) +
  geom_point() + 
  theme_minimal() # theme options: https://ggplot2.tidyverse.org/reference/ggtheme.html
```

---

## Plot and text

.pull-left[
- Some text
- goes here
]
.pull-right[
```{r warning=FALSE, out.width="100%", fig.width=4, echo=FALSE}
# see how I changed out.width and fig.width from defaults
# to make the figure bigger
ggplot(penguins, aes(x = bill_length_mm, y = species, color = species)) +
  geom_boxplot() +
  theme_minimal()
```
]

---

# Tables

If you want to generate a table, make sure it is in the HTML format (instead of Markdown or other formats), e.g.,

```{r iris-table, echo = FALSE}
kable(head(iris), format = "html")
```

---

# Images

```{r castle, echo = FALSE, out.width = "60%", fig.align = "center", fig.cap = "Image credit: Photo by Jörg Angeli on Unsplash."}
include_graphics("https://images.unsplash.com/photo-1535448033526-c0e85c9e6968?ixlib=rb-1.2.1&ixid=eyJhcHBfaWQiOjEyMDd9&auto=format&fit=crop&w=1650&q=80")
```

Or you can also include a full page image. See next slide.

---

background-image: url(https://images.unsplash.com/photo-1535448033526-c0e85c9e6968?ixlib=rb-1.2.1&ixid=eyJhcHBfaWQiOjEyMDd9&auto=format&fit=crop&w=1650&q=80)

---

# Math Expressions

You can write LaTeX math expressions inside a pair of dollar signs, e.g. &#36;\alpha+\beta$ renders $\alpha+\beta$. You can use the display style with double dollar signs:

```
$$\bar{X}=\frac{1}{n}\sum_{i=1}^nX_i$$
```

$$\bar{X}=\frac{1}{n}\sum_{i=1}^nX_i$$

Limitations:

1. The source code of a LaTeX math expression must be in one line, unless it is inside a pair of double dollar signs, in which case the starting `$$` must appear in the very beginning of a line, followed immediately by a non-space character, and the ending `$$` must be at the end of a line, led by a non-space character;

1. There should not be spaces after the opening `$` or before the closing `$`.

1. Math does not work on the title slide (see [#61](https://github.com/yihui/xaringan/issues/61) for a workaround).

---

# Feeling adventurous?

- Want to find out more about `xaringan`? See https://slides.yihui.name/xaringan/#1.

- You are welcomed to use the default styling of the slides. In fact, that's what I expect majority of you will do. You will differentiate yourself with the content of your presentation.

- But some of you might want to play around with slide styling. The 
`xaringanthemer` provides some solutions for this that: https://pkg.garrickadenbuie.com/xaringanthemer.

- And if you want more bells and whistles, there is also `xaringanExtra`: https://pkg.garrickadenbuie.com/xaringanExtra.
